\addcontentsline{toc}{section}{\texorpdfstring{Tài liệu}{Tai lieu}}

\small

\begin{thebibliography}{10}
\bibitem{VietTUG}
ViệtTUG.
\newblock {Cộng đồng người Việt sử dụng \TeX{}}.
\newblock \url{http://www.viettug.org/}.

\bibitem{HA-prosper}
Hendri Adriaens.
\newblock \pf{HA-prosper} package.
\newblock \url{CTAN:/macros/latex/contrib/HA-prosper}.

\bibitem{xkeyval}
Hendri Adriaens.
\newblock \pf{xkeyval} package.
\newblock \url{CTAN:/macros/latex/contrib/xkeyval}.

\bibitem{random}
Donald Arseneau.
\newblock \texttt{random.tex}.
\newblock \url{CTAN:/macros/generic/misc}.

\bibitem{enumitem}
Javier Bezos.
\newblock \pf{enumitem} package.
\newblock \url{CTAN:/macros/latex/contrib/enumitem}.

\bibitem{graphics}
David Carlisle.
\newblock \pf{graphics} bundle.
\newblock \url{CTAN:/macros/latex/required/graphics}.

\bibitem{LyXWeb}
{\LyX\ crew}.
\newblock {\LyX\ website}.
\newblock \url{http://www.lyx.org}.

\bibitem{CTAN}
CTAN crew.
\newblock {The Comprehensive TeX Archive Network}.
\newblock \url{http://www.ctan.org}.

\bibitem{natbib}
Patrick~W. Daly.
\newblock \pf{natbib} package.
\newblock \url{CTAN:/macros/latex/contrib/natbib}.

\bibitem{prosper}
Fr\'ed\'eric Goualard and Peter~M\o ller Neergaard.
\newblock \pf{prosper} class.
\newblock \url{CTAN:/macros/latex/contrib/prosper}.

\bibitem{xcolor}
Uwe Kern.
\newblock \pf{xcolor} package.
\newblock \url{CTAN:/macros/latex/contrib/xcolor}.

\bibitem{extsizes}
James Kilfiger and Wolfgang May.
\newblock \pf{extsizes} bundle.
\newblock \url{CTAN:/macros/latex/contrib/extsizes}.

\bibitem{companion}
Frank Mittelbach and Michel Goossens.
\newblock {\em The {\LaTeX} Companion}.
\newblock Tools and Techniques for Computer Typesetting. Addison-Wesley,
  Boston, Massachusetts, 2 edition, 2004.
\newblock With Johannes Braams, David Carlisle, and Chris Rowley.

\bibitem{hyperref}
Sebastian Rahtz and Heiko Overdiek.
\newblock \pf{hyperref} package.
\newblock \url{CTAN:/macros/latex/contrib/hyperref}.

\bibitem{geometry}
Hideo Umeki.
\newblock \pf{geometry} package.
\newblock \url{CTAN:/macros/latex/contrib/geometry}.

\bibitem{PSTricksWeb}
Herbert Vo\ss.
\newblock \pf{PSTricks} website.
\newblock \url{http://pstricks.tug.org}.

\bibitem{PSTricks}
{Timothy Van} {Zandt et al.}
\newblock \pf{PSTricks} package, v1.07, 2005/05/06.
\newblock \url{CTAN:/graphics/pstricks}.
\end{thebibliography}
\endinput
